\section{Innovative Features}
\label{sec:innovative_features}

% BEGIN SECTION

To supplement the language detector application’s base functionality, the system introduces two innovative features: photographic text recognition and language datasheets.\\

At the base level, users type out the text they wish to inquire about. However, there is a flaw with this method – if the user does not recognize the language, it is highly unlikely that they have a keyboard that supports its alphabet. Even if they do, they lack the knowledge to write out the characters quickly. The lack of intuition behind this input method incentivizes users to use competitor apps instead, taking away from the company’s revenue. So to rectify this concern, instead of requesting a whole typed out string from the user, the photo recognizer simply takes one picture as input, and internally extracts the writing. With the snap of one picture, the system autonomously identifies the correct language, making it the most convenient option available. This way, it sustains all of its users, leading to increased usage and revenue.\\

To further enhance the user experience, the system displays informational datasheets corresponding to the languages when they are scanned. Queries are rewarded with a comprehensive set of fun facts about the language’s scripts, history, speakers, and with prominent regions that speak the language pinpointed on a map.\\

Overall, the superior ease of use and informativity when identifying the language separates this app from alternatives. These benefits drive more users to the app, and in turn, increases revenue for the company.\\  

Some other features that are considered in future updates include: 
\begin{itemize}
    \item Translator Service
    \item Audio Interpreter
    \item Profile Feature to track app usage and recent scans 
    \item Language Quizzes
    \begin{itemize}
        \item One vs One with Friends 
        \item Global Tournaments
    \end{itemize}
    \item Geo-Assigning Languages based on High Scan Locations 
    \begin{itemize}
        \item For example, if a French speaking student is planning to attend McMaster University and sees a lot of students scan French text east of the university, whereas the west is more English dominated, they might choose to move into the eastern part as it's likely that more people of the same culture live there. 
    \end{itemize}
    \item Machine Learning Model Expert
\end{itemize}

% END SECTION