\item Identify the Language \\
	\textbf{Precondition:} User is unfamiliar with the language when browsing his/her device and decides to copy and paste said text into the app.
	\begin{enumerate}[{\bf VP1:}]
		% VIEWPOINT USER FOR BE1
		\item Users \\
				\textbf{Main Success Scenario:}
					\begin{enumerate}[{\bf 1.}]
						\item User enters the app.
						\item User taps the button to identify the language.
							\item System prompts user for input.
							\item User chooses type of input.
							\item User uploads the input onto the app (see BE2 for more details).
							\item System interprets the input.
							\item System outputs the most correct language.
					\end{enumerate}
				
					\textbf{Secondary Scenario:} System failed to identify language \\
					\textbf{7.i.} System is unable to identify the language with 80\% certainty.\\
					\textbf{7.i.1.} System is unable to provide an 80\% accurate answer. \\
					\textbf{7.i.2.} System asks the user for more input (proceed to step 8 or 9).
					
					\textbf{8.} User accepts to give more input.
					\begin{enumerate}[{\bf 8.1.}]
						\item Return and repeat steps 4 to 7.
					\end{enumerate}
					\textbf{9.} User declines to give more input.
					\begin{enumerate}[{\bf 9.1.}]
						\item System outputs the most correct answer, but with a notice of less than 80\% certainty.
					\end{enumerate}
					\textbf{Post-Condition}:
					\\ User is familiarized with the language 
			\item Administrators - \textbf{N/A}
			\item Linguistic Enthusiasts - \textbf{N/A}
			\item Language Translator Companies - \textbf{N/A}
		\end{enumerate}
	\textbf{Global Scenario}:
	\\ \textbf{Precondition}: User is unfamiliar with the langiage when browsing his/her device and decides to copy and paste said text into the app
	\\ \textbf{Main Success Scenario}:
	\begin{enumerate}[{\bf 1.}]
		\item User enters the app
		\item User taps the button identify Language
		\item System prompts user for input
		\item User choose input type
		\item User upload the input onto the app
		\item System process the input
		\item System outputs the most correct language
	\end{enumerate}
	\textbf{Secondary Scenario}: System failed to identify the language
	\begin{enumerate}[{\bf 7.i.}]
		\item System asks for more input from the user
		\item User accepts to give more input
		\item Return and Repeat Steps 4-7
	\end{enumerate}
	\begin{enumerate}[{\bf 7.ii.}]
		\item User declines to give more input
	\end{enumerate}
	\textbf{Post-Condition}: User is familiarized with the language